Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-10-27 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

date: "`r format(Sys.time(), '%d, %B, %Y')`"
documentclass: article
papersize: letter
fontsize: 12pt
bibliography: citations.bib
biblio-style: asa
output: pdf_document
---
#Abstract: 
The 2020 NBA playoffs were played inside of a bubble in Disney World because of
the COVID-19 pandemic. This meant that there would be no fans in attendance, 
games played on neutral courts and no traveling for teams which in theory 
removes home-court advantage from the games. This idea was a hot topic of 
discussion as analysts and fans debated the possible effects it may have on the
outcome of games. Home-court advantage has historically played a huge role in 
NBA playoff series outcomes. Thus, to study the effects of the bubble, and 
home-court advantage, the 2020 season is compared to the 2017, 2018, and 2019
playoffs. While many factors contribute to the outcome of games, points scored
is the deciding factor of who wins games so scoring will be the primary focus 
of this study. The specific measures of interest are team scoring totals and 
team shooting percentage on two pointers, three pointers, and free throws. 
Comparing these measures for home teams and away teams in 2020 vs. 2017-2019
shows how the 2020 playoffs favored away teams more than normal, particularly
with two point shooting and total scoring.

@@

titles <- c(2020, "2017-19", "95% CI Low", "95% CI Up", "Test Statistic", "P-value")
rows <- c("Home Team Win %", "Home Team Scoring", "Away Team Scoring", "Home Team 2P%", "Home Team 3P%",
          "Home Team FT%", "Away Team 2P%", "Away Team  3P%", "Away Team FT%")
results <- data.frame(rowone, rowtwo, rowthree, rowfour, rowfive, rowsix,
                    rowseven, roweight, rownine, stringsAsFactors = FALSE)
resultsfinal <- data.frame(t(results))
resultsfinal <- round(resultsfinal, 4)
colnames(resultsfinal) <- titles
row.names(resultsfinal) <- rows

>>>>

date: "`r format(Sys.time(), '%d, %B, %Y')`"
documentclass: article
papersize: letter
fontsize: 12pt
bibliography: citations.bib
biblio-style: asa
output: pdf_document
---
Abstract: 
The 2020 NBA playoffs were played inside of a bubble in Disney World because of
the COVID-19 pandemic. This meant that there would be no fans in attendance, 
games played on neutral courts and no traveling for teams which in theory 
removes home-court advantage from the games. This idea was a hot topic of 
discussion as analysts and fans debated the possible effects it may have on the
outcome of games. Home-court advantage has historically played a huge role in 
NBA playoff series outcomes. Thus, to study the effects of the bubble, and 
home-court advantage, the 2020 season is compared to the 2017, 2018, and 2019
playoffs. While many factors contribute to the outcome of games, points scored
is the deciding factor of who wins games so scoring will be the primary focus 
of this study. The specific measures of interest are team scoring totals and 
team shooting percentage on two pointers, three pointers, and free throws. 
Comparing these measures for home teams and away teams in 2020 vs. 2017-2019
shows how the 2020 playoffs favored away teams more than normal, particularly
with two point shooting and total scoring.

@@

titles <- c(2020, "2017-19", "95% CI LL", "95% CI UL", "Test Stat.", "P-value")
rows <- c("Home Team Win %", "Home Team Scoring", "Away Team Scoring", "Home Team 2P%", "Home Team 3P%",
          "Home Team FT%", "Away Team 2P%", "Away Team  3P%", "Away Team FT%")
results <- data.frame(rowone, rowtwo, rowthree, rowfour, rowfive, rowsix,
                    rowseven, roweight, rownine, stringsAsFactors = FALSE)
resultsfinal <- data.frame(t(results))
resultsfinal <- round(resultsfinal, 4)
colnames(resultsfinal) <- titles
row.names(resultsfinal) <- rows
